Meta-analysis

### 2019-08-01 05_MetaAnalysis.Rmd
Corrected the yeild error prediction models to have yield error as the response. Also investigated a fully random model

library(lme4)
library(scales)
# Run a linear model with Yield error as a fixed effect predictor and Trial as a random intercept
PM_MB_trianLMER <- lmer(log(Yield_error) ~ `grain_yield.t.ha.`+ 
         (1|Trial_ref), data = PM_MB_train)

summary(PM_MB_trianLMER)

paramA <- (summary(PM_MB_trianLMER)$coef)[2,1] # Extract the Slope to predict Yield error
InterC <- (summary(PM_MB_trianLMER)$coef)[1,1] # Extract the intercept to predict Yield error

lmer.coef <- coef(PM_MB_trianLMER)

# plot of the mixed effect model, Black line shows the mean lmer regression line
ggplot(PM_MB_train)+
   geom_point(aes(y = log(`grain_yield.t.ha.`), x = Yield_error, colour = Trial_ref))+
   geom_abline(intercept = c(InterC,lmer.coef$Trial_ref[,1]), 
               slope = c(paramA,lmer.coef$Trial_ref[,2]),
               size = 1.5,
               colour = c("Black",hue_pal()(6)))

for(i in NATrials$Trial_ref){
Sv <- (log(PM_MB_means[PM_MB_means$Trial_ref == i,]$`grain_yield.t.ha.`) - InterC)/ paramA

PM_MB_means[PM_MB_means$Trial_ref == i,]$Yield_error <- Sv
PM_MB_means[PM_MB_means$Trial_ref == i,]$Y_error.type <- "SamplingVariance"
print(Sv)

@@

Just for kicks lets look at the linear regression model as a Random effects model where `Yield_error` is set as a random slope to the random intercept `Trial_ref`.  
The model fits better as shown by an anova comparison. But now to determine how to impute from this model ....
```{r random_slope_model}

# Run a linear model with Yield error as a fixed effect predictor and Trial as a random intercept
PM_MB_trianLMERx <- lmer(log(`grain_yield.t.ha.`) ~ 1 + 
         (Yield_error|Trial_ref), data = PM_MB_train)

anova(PM_MB_trianLMER,PM_MB_trianLMERx) # random slope model signigicantly better

@@

InterC <- (summary(PM_MB_trianLMER)$coef)[1,1] # Extract the intercept to predict Yield error

lmer.coef <- coef(PM_MB_trianLMERx)

# plot of the mixed effect model, Black line shows the mean lmer regression line
ggplot(PM_MB_train)+
   geom_point(aes(y = log(`grain_yield.t.ha.`), x = Yield_error, colour = Trial_ref))+
   geom_abline(intercept = lmer.coef$Trial_ref[,2], 
               slope = lmer.coef$Trial_ref[,1],
               size = 1.5,
               colour = hue_pal()(6))

@@

>>>>

library(lme4)
library(scales)
# Run a linear model with Grain_yield as a fixed effect predictor and Trial as a random intercept
PM_MB_trianLMER <- lmer(Yield_error ~ `grain_yield.t.ha.`+ 
         (1|Trial_ref), data = PM_MB_train)
summary(PM_MB_trianLMER)

# grain yeild is a significant predictor for yeild error (t value = -2.757)
# does log transformation improve the model

PM_MB_trianLMER.1 <- lmer(log(Yield_error) ~ `grain_yield.t.ha.`+ 
         (1|Trial_ref), data = PM_MB_train)
summary(PM_MB_trianLMER.1) # grain yeild is not a significant predictor of log(yeild error)
anova(PM_MB_trianLMER, PM_MB_trianLMER.1) # no significant difference between the models

PM_MB_trianLMER.2 <- lmer(Yield_error ~ log(`grain_yield.t.ha.`)+ 
         (1|Trial_ref), data = PM_MB_train)
summary(PM_MB_trianLMER.2) # log(grain yeild) is a significant predictor of yeild error
anova(PM_MB_trianLMER, PM_MB_trianLMER.2) # no significant difference between the models

#log transforming the response or predictor variables did not improve the model therefore I will leave it untransformed
# I will be using the first model PM_MB_trianLMER for further analyses beyond this point

paramA <- (summary(PM_MB_trianLMER)$coef)[2,1] # Extract the overall mean Slope to predict Yield error
InterC <- (summary(PM_MB_trianLMER)$coef)[1,1] # Extract the overall mean intercept to predict Yield error

lmer.coef <- coef(PM_MB_trianLMER) # extracting the mean random intercept for each of trial variables

# plot of the mixed effect model, Black line shows the mean lmer regression line
ggplot(PM_MB_train)+
   geom_point(aes(y = Yield_error, x = `grain_yield.t.ha.`, colour = Trial_ref))+
   geom_abline(intercept = c(InterC,lmer.coef$Trial_ref[,1]), 
               slope = c(paramA,lmer.coef$Trial_ref[,2]),
               size = 1.5,
               colour = c("Black",hue_pal()(6)))+
   coord_cartesian(xlim = c(0.8, 1.2))

for(i in NATrials$Trial_ref){
#Sv <- (log(PM_MB_means[PM_MB_means$Trial_ref == i,]$`grain_yield.t.ha.`) - InterC)/ paramA  # parameter from when I had the predictor and response variable flipped

Sv <- (PM_MB_means[PM_MB_means$Trial_ref == i,]$`grain_yield.t.ha.` * paramA) + InterC

PM_MB_means[PM_MB_means$Trial_ref == i,]$Yield_error <- Sv
PM_MB_means[PM_MB_means$Trial_ref == i,]$Y_error.type <- "SamplingVariance"

@@

Just for kicks lets look at the linear regression model as a Random effects model where `grain_yield.t.ha.` is set as a random slope to the random intercept `Trial_ref`.  
The model fits better as shown by an anova comparison. But now to determine how to impute from this model ....
```{r random_slope_model}

# Run a linear model with Yield error as a fixed effect predictor and Trial as a random intercept
PM_MB_trianLMERx <- lmer(Yield_error ~ 1 + 
         (`grain_yield.t.ha.`|Trial_ref), data = PM_MB_train)

anova(PM_MB_trianLMER,PM_MB_trianLMERx) # random slope model significantly better # P = 0.00378

@@

InterC <- (summary(PM_MB_trianLMER)$coef)[1,1] # Extract the overall mean intercept

lmer.coefx <- coef(PM_MB_trianLMERx)

# plot of the mixed effect model, Black line shows the mean lmer regression line
ggplot(PM_MB_train)+
   geom_point(aes(y = Yield_error, x = `grain_yield.t.ha.`, colour = Trial_ref))+
   geom_abline(intercept = lmer.coefx$Trial_ref[,2], 
               slope = lmer.coefx$Trial_ref[,1],
               size = 1.5,
               colour = hue_pal()(6))+
   coord_cartesian(xlim = c(0, 3))

@@

What is interesting about this model is the slopes all converge and pass through a specific point.
We can use this to predict the slope of the trials we don't know the specific slope for and get a better prediction of the errors.

```{r imputing_from_randomModel}
ggplot(PM_MB_train)+
   geom_point(aes(y = Yield_error, x = `grain_yield.t.ha.`, colour = Trial_ref))+
   geom_abline(intercept = lmer.coefx$Trial_ref[,2], 
               slope = lmer.coefx$Trial_ref[,1],
               size = 1.5,
               colour = hue_pal()(6))+
   coord_cartesian(xlim = c(2.85, 2.875), ylim = c(0.0048,0.0049))

# let us find the value of this point
# what are the slopes and intercepts for each random grouping factor (Trial_ref)
randomS_coefs <- lmer.coefx$Trial_ref

# lets write a funcion to generate a sequence of predicted Y (yield error) values
slope_generator <- function(slope,intercept, x_minimum = 0.8, x_maximum = 1.2, increment = 0.00000001){
   Xi <- seq(from = x_minimum, to = x_maximum, by = increment)
   (Xi * slope) + intercept
}

# generate a vector of predicted values for each of the trial slopes, returned as a matrix
tmp2 <- apply(randomS_coefs,1,FUN = function(x) {
   slope_generator(slope = x[1], intercept = x[2],x_minimum = 2.86135, x_maximum = 2.8614)
                      })
head(tmp2)

# find which X predictor gives the lowest variation between trials and therefore the closest to the point at which the slopes converge
tmp3 <- apply(tmp2,1,sd)
plot(tmp3)
min(tmp3)
x_3252 <- which(tmp3 == min(tmp3))

# zooming in on the X predictor by increasing resolution
seq(from = 2.85,to = 2.875, by =0.0001)[115]
seq(from = 2.85,to = 2.875, by =0.00001)[1139]
x_point <- seq(from = 2.86135,to = 2.8614, by =0.00000001)[x_3252]

# predict the y (yeild error) at the x predictor (grain.yield) for each trial group
tmp4 <- apply(randomS_coefs,1,FUN = function(x){
   (x_point * x[1]) + x[2]
})

# they are all the same value but lets take the mean to be more precise
y_point <- mean(tmp4)

# here is my 'good-enough' prediction of the convergence point
common_S_coordinate <- c(x_point, y_point)
